### 2015-03-02 fundamentals/impl.tex
spellcheck
I think this solves #85 with the 'changing all the text' strategy.

Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchical relationship, where parents can
choose to \textit{deploy} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power
very simply. The \gls{API} provides the \Class{Agent} with helpful functionality for
interacting with the \Cyclus simulation kernel while abstracting away unnecessary
detail.

@@

Multiple strategies, collectively known as \emph{\gls{QA}}, have
been invented to mitigate structural and algorithmic errors
in software. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, testing, and others.

@@

@@

@@

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign if the
simulator does not work as intended on a new system.
Testing serves a critical role in \gls{QA} because it directly compares the
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration
tests, and regression tests.  It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.

@@

Unit tests compare the results of the smallest code \emph{unit}, typically a
single function or a class.  \Cyclus uses the Google Test framework
\cite{inc_googletest_2008} as a harness for running unit tests. Sufficient unit
tests are required for any proposed change to the \Cyclus code base. Currently,
\Cyclus implements over 450 unit tests and \Cycamore implements 85.  These
cover approximately 65\% of their respective code bases, and these numbers are
expected to grow over time.

@@

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other.  By analogy,
simply because the gears (units) are made correctly does not imply that the
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios that are sufficiently simple to predict the results
and verifying that results match those predictions. A set of standard input
files are run, then the output is inspected and compared via Nose
\cite{pellerin_nose_2007}, a Python test framework.  In this way, \Cyclus code
units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.

@@

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed.

@@

All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
\gls{QA} policy. This certifies that the intended goals of an \gls{API} are communicated
explicity by the author in prose form. Future developers are then able to
compare the implementation versus the documentation to discern whether or not
these are in agreement. Documentation is thus a secondary higher-level information
stream.  In \Cyclus, this information is aggregated together into static
websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx
\cite{brandl_sphinx_2014}
tools, and can be accessed at \url{http://fuelcycle.org}.

>>>>

Interchangeability is accomplished by providing inheritable \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction. For example,
an archetype that inherits the \Class{Region} interface, as in Figure
\ref{fig:agent_uml}, is interchangeable with any other Region agent.
For the archetype developer, this interface provides enormous power
very simply. The \gls{API} abstracts away unnecessary detail while providing
all necessary functionality for interacting with the \Cyclus simulation kernel.

@@

Multiple strategies, collectively known as \emph{\gls{QA}}, have
been invented to mitigate structural and algorithmic errors
in software. These include \emph{\gls{VV}}
\cite{boehm_software_1989}, \emph{\gls{UQ}}
\cite{sacks_design_1989}, testing, and others.

@@

Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation of the \Cyclus core in a general sense is infeasible as it is contingent on the archetypes comprising a simulation, and to be meaningful \gls{UQ} must likewise extend beyond the kernel.

@@

Lastly, \gls{UQ} is a process that is used on specific simulation
instantiations to statistically determine quality. \gls{UQ} is a process that applies
to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
cycle. Any \gls{UQ} results are applicable only to the scenario that is under
analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
and in the domain of the expert user.

@@

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign if the
simulator does not work as intended on a new system.
Testing serves a critical role in \gls{QA} because it directly compares the
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration
tests, and regression tests.

It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.  Of course, test code is
just as likely to contain errors as the code it is designed to test.
However, it is assumed that diligence and one level of testing
is sufficient to meet the aims of \gls{QA} and prevent an infinite recursion
of testing-the-tests.

@@

Unit tests compare the results of the smallest code \emph{unit},
typically a single function or a class. What constitutes the smallest code
unit depends on the context of the specific unit in question. While this is
an ambiguous definition, when combined with a philosophy of keeping units as small
as possible, it is often clear in practice what needs to be tested.

\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit
tests. Sufficient unit tests are required for any proposed change to the \Cyclus
code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.

@@

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other.  By analogy,
simply because the gears (units) are made correctly does not imply that the
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios that are sufficiently simple to predict the results and verifying
        that results match those predictions. A set of standard input files have thus been constructed.
Python is used to run the same set of \Cyclus simulations as a subprocess for each integration test.
 The results are then inspected and compared via Nose \cite{pellerin_nose_2007}, a Python test framework.
In this way, \Cyclus code units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.

@@

Regression tests ensure significant unintended changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting simulations.

@@

All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
\gls{QA} policy. This certifies that the intention for a code unit is communicated
in way that is separate from its implementation. This policy is important
because implementations are often wrong and do not reliably communicate their intent. Truly trustworthy communication about what
software should be doing occurs when the author explicitly states the
goals of an \gls{API} in prose form. Future developers are then able to
compare the implementation versus the documentation to discern whether or not
these are in agreement. Documentation is thus a secondary higher-level information
stream.  In \Cyclus, this information is aggregated together into static
websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx
\cite{brandl_sphinx_2014}
tools, and can be accessed at \url{http://fuelcycle.org}.
